Hadoop Image Processing Framework

### 2015-03-14 Paper.tex
Further language edits.

	When considering operations such as face detection, image classification\cite{Li2009} and other types of processing on images, there are limits on what can be done to improve performance of single computers to make them able to process information at the scale of social media. Therefore, the advantages of parallel distributed processing of a large image dataset by using the computational resources of a cloud computing environment should be considered. In addition, if computational resources can be secured easily and relatively inexpensively, then cloud computing is suitable for handling large image data sets at very low cost and increased performance. Hadoop, as a system for processing large numbers of images by parallel and distributed computing, seems promising. In fact, Hadoop is in use all over the world. Studies using Hadoop have been performed, dealing with text data files\cite{Lin2010}, analyzing large volumes of DNA sequence data\cite{McKenna2010}, converting the data of a large number of still images to PDF format, and carrying out feature selection/extraction in astronomy\cite{wiley2011}. %Cite the papers in which these examples appear
These examples demonstrate the usefulness of the Hadoop system, which can run multiple processes in parallel for load balancing and task management.

@@

	\section{Related Work}
	With rapid increase of usage of online photo storage and social media like facebook, flickr and picasa the amount of image data available is larger than ever before. The amount of image data is growing rapidly every day. According to Buzzfeed for every minute 27800 photos are uploaded to Instagram. As per facebook, they get 208,300 photos uploaded every minute\cite{Horaczek2013}. This alone provides a plethora of image that can scale up to billions of images. It is these reasons that motivate the need for research with image processing applications that take advantage of large sets of images

	A brief overview of previous work sharing the themes of image processing and distributed computation is presented below:

	Web-Scale Computer Vision using MapReduce for Multimedia Data Mining \cite{White2010} present a case study of classifying and clustering billions of regular images using MapReduce. A way of pre-processing images for use in a sliding-window approach for object recognition is described. Distributed High Performance Video Processing in the cloud, outlines some of the limitations of the MapReduce model when dealing with high-speed video encoding, namely its dependence on the NameNode as a single point of failure, and lack of possibility for generalization in order to suit the issue at hand. An alternate optimized implementation is proposed for providing cloud-based IaaS (Infrastructure as a Service) Solution. In Parallel K-Means clustering of Remote Sensing Images Based on MapReduce \cite{Lv2010} describe using the k-means algorithm in conjunction with MapReduce and satellite/aerophoto images in order to find different elements based on their color. Using Transaction Based Parallel computing to solve image processing and computational physics problems by Harold describes the use of distributed computing with two examples video processing and subsurface transport. There was no information provided on how image processing parts of the examples.

@@

\section{Methodology}
Hadoop Image processing Framework is created to provide users a tool to develop a large scale image processing applications with ease.

The main goals of Hadoop Image Processing framework:
\begin{itemize}
	\item Provide an open source framework over Hadoop MapReduce for developing large scale image applications 
	\item Flexibility to store images in various Hadoop File Formats
	\item Present users with an intuitive interface for image based operations which are highly parallelized and balanced and hide the high technical details of hadoop MapReduce Framework
	\item Allow interoperability between various image processing libraries
\end{itemize}

\subsection{Downloading and storing image data}
Hadoop's distributed file system(HDFS) to store files in various nodes throughout the cluster. Storing small files\cite{White2009} is a big problem in Hadoop. A small file is one which is significantly smaller than HDFS block size. As the large image dataset can have many number of small files and the problem is HDFS cant handle lots of files. The problem can be solved by providing some kind of container to group the files in some way. Hadoop offers a few options:
\begin{itemize}
	\item HAR File
	\item Sequence File
	\item Map File
\end{itemize}

The Downloader Module of the framework does the following work

>>>>

When considering operations such as face detection, image
classification\cite{Li2009} and other types of processing on images,
there are limits on what can be done to improve performance of single
computers to make them able to process information at the scale of
social media. Therefore, the advantages of parallel distributed
processing of a large image dataset by using the computational
resources of a cloud computing environment should be considered. In
addition, if computational resources can be secured easily and
relatively inexpensively, then cloud computing is suitable for
handling large image data sets at very low cost and increased
performance. Hadoop, as a system for processing large numbers of
images by parallel and distributed computing, seems promising. In
fact, Hadoop is in use all over the world. Studies using Hadoop have
been performed, dealing with text data files\cite{Lin2010}, analyzing
large volumes of DNA sequence data\cite{McKenna2010}, converting the
data of a large number of still images to PDF format, and carrying out
feature selection/extraction in astronomy\cite{wiley2011}.  These
examples demonstrate the usefulness of the Hadoop system, which can
run multiple processes in parallel for load balancing and task
management.

@@

\section{Related Work}
With the rapid usage increase of online photo storage and social media
on sites like Facebook, Flickr and Picasa, more image data is
available than ever before, and is growing every day.  Every minute
27800 photos are uploaded to Instagram, while Facebook receives
208,300 photos over the same time frame.\cite{Horaczek2013} This alone
provides a source of image data that can scale into the billions.  The
explosion of available images on social media has motivated image
processing research and application development that can take
advantage of very large image data stores.

\cite{White2010} presents a case study of classifying and clustering billions of regular images using MapReduce. It describes an image pre-processing technique for use in a sliding-window approach for object recognition.  Distributed High Performance Video Processing in the cloud outlines some of the limitations of the MapReduce model when dealing with high-speed video encoding, namely its dependence on the NameNode as a single point of failure, and lack of possibility for generalization in order to suit the issue at hand. An alternate optimized implementation is proposed for providing cloud-based IaaS (Infrastructure as a Service) Solution. In Parallel K-Means clustering of Remote Sensing Images Based on MapReduce \cite{Lv2010} describe using the k-means algorithm in conjunction with MapReduce and satellite/aerophoto images in order to find different elements based on their color. Using Transaction Based Parallel computing to solve image processing and computational physics problems by Harold describes the use of distributed computing with two examples video processing and subsurface transport. There was no information provided on how image processing parts of the examples.

@@

\section{Methodology}
The Hadoop Image Processing Framework is intended to provide users
with an accessible, easy-to-use tool for developing large-scale image
processing applications.

The main goals of the Hadoop Image Processing Framework are:
\begin{itemize}
\item Provide an open source framework over Hadoop MapReduce for
  developing large-scale image applications
\item Provide the ability to flexibly store images in various Hadoop
  file formats
\item Present users with an intuitive application programming
  interface for image-based operations which is highly parallelized
  and balanced, but which hides the technical details of Hadoop
  MapReduce
\item Allow interoperability between various image processing
  libraries
\end{itemize}

\subsection{Downloading and storing image data}
Hadoop uses the Hadoop Distributed File System (HDFS) to store files
in various nodes throughout the cluster.  One of Hadoop's significant
problems is that of small file storage. \cite{White2009} A small file
is one which is significantly smaller than HDFS block size.  Large
image datasets are made up of small image files in great numbers,
which is a situation which HDFS has a great deal of trouble
handling. The problem can be solved by providing a container to group
the files in some way. Hadoop offers a few options:
\begin{itemize}
	\item HAR File
	\item Sequence File
	\item Map File
\end{itemize}

The Downloader Module of our Hadoop Image Processing Framework
performs the following operations:
